---
title: "Weight of Fish"
author: "Adriana Lopez"
date: "Spring 2021"
output: 
  html_document:
    number_sections: true
    toc: true
---
  

```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(car)
Allfish <- read.csv(file = "Fish.csv")
Allfish$Species <- as.factor(Allfish$Species)
levels(Allfish$Species)
```

```{r}
Perch <- subset(Allfish, Species == "Perch")
Perch <- select(Perch, -Species)
Bream <- subset(Allfish, Species == "Bream")
Bream <- select(Bream, -Species)
Smelt <- subset(Allfish, Species == "Smelt")
Smelt <- select(Smelt, -Species)
```


# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

## Build the best regression model you can that predicts the weight of perch
## Using only two predictor variables  


# Perch

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

From the plot above we see that the best regression model is height and width.  
The model of height and  width are the adjusted $r^2$ of about 0.9400.  

## Which is best??  

```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[2,]
```
```{r}
PerchModel <- lm(Weight~Height+Width, data= Perch )
summary.lm(PerchModel)
```

Here we get that the adjusted $^2$ is 0.94 which is the best model because $r^2$ is the highest. The residual standard error is 85.17.

# Bream

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Bream,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

From the plot above we see that the best three regression model is Length1, width, and height.  
The model of height, width, and length1 are the adjusted $r^2$ of about 0.940.  

## Which is best??  

```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[2,]
```
```{r}
BreamModel <- lm(Weight~Height+Length2, data= Bream )
summary.lm(BreamModel)
```

The adjusted $r^2$ of height and length2 is 0.9356. The residual standard error of the two best regression model is 53.1.



# Smelt

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Smelt,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```


The best model for predicting weight of Smelt using two variables is Length2 and Width.The $r^2$ is 0.96.  

## Which is best??  

```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[2,]
```
```{r}
SmeltModel <- lm(Weight~Length2+Width, data= Smelt )
summary.lm(SmeltModel)
```
  


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->


The Perch plot above we see that the best regression model is height and width.The model of height and  width are the adjusted $r^2$ of about 0.9400. For Bream From the plot above we see that the best three regression model is Length1, width, and height. The model of height, width, and length1 are the adjusted $r^2$ of about 0.940. For Smelt the best model for predicting weight of Smelt using two variables is Length2 and Width.The $r^2$ is 0.96.  
